### 2014-12-16 main.tex
Finished pathways, copy & past chapters 3 and 4.
Refactor rules
Merge changes
Adding popular introduction, title and new abstract
Editing introduction chapter
Add dataflow example to introduction
Finish introduction chapter and restructure the rest
Early work on chapter 3
Chapter 3: Implicit parameters and distributed
Flat coeffect systems in Chapter 03
Working on structural liveness (Chapter 3)
Semantics of structural liveness (Chapter 3)
Tweak style and finish Chapter 3
Start working on Chapter 4
Categorical semantics of flat calculus (Chapter 4)
Syntactic properties (Chapter 4)
Call-by-valu

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

@@

% Includes the file which contains all the document configurations and packages - make sure to edit this file
\input{classicthesis-config}
\usepackage{semantic}
\usepackage{paralist}
\usepackage{etoolbox}
\usepackage{stmaryrd}
\usepackage{amssymb}

\newtheorem{definition}{Definition}

% source code & types
\newcommand{\sep}[0]{\;\; | \;\;}
\newcommand{\kvd}[1]{\textnormal{\bfseries\sffamily #1}} %
\newcommand{\str}[1]{\textnormal{\ttfamily #1}} %
\newcommand{\ident}[1]{\textnormal{\sffamily #1}}
\newcommand{\ctyp}[2]{C^{#1}#2}
\newcommand{\mtyp}[2]{M^{#1}#2}
\newcommand{\subst}[3]{#1[#2 \leftarrow #3]}

@@

\newcommand{\codesnip}[0]{\renewcommand{\baselinestretch}{0.9}\normalsize}
\newcommand{\codesnipout}[0]{\renewcommand{\baselinestretch}{1.0}\normalsize}

% Half line spacing around align
\newcommand{\zerodisplayskips}{%
  \setlength{\abovedisplayskip}{0.5em}
  \setlength{\belowdisplayskip}{0.5em}
  \setlength{\abovedisplayshortskip}{0.5em}
  \setlength{\belowdisplayshortskip}{0.5em}}
\appto{\normalsize}{\zerodisplayskips}
\appto{\small}{\zerodisplayskips}
\appto{\footnotesize}{\zerodisplayskips}

@@

% \include{FrontBackMatter/Titlepage} % Main title page

@@

% \cleardoublepage\include{FrontBackMatter/Abstract} % Abstract page

% \cleardoublepage\include{FrontBackMatter/Publication} % Publications from the thesis page

@@

\include{text/Chapter01} % Chapter 1
\include{text/Chapter02} % Chapter 2

% \include{Chapters/Chapter03} % Chapter 3
%\include{Chapters/Chapter04} % Chapter 4 - empty template

@@

% \appendix

@@

% \include{Chapters/Chapter0A} % Appendix A
%\include{Chapters/Chapter0B} % Appendix B - empty template

@@

>>>>

%%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

@@

% Includes the file which contains all the document configurations and packages - make sure to edit this file
\input{classicthesis-config}
\usepackage{semantic}
\usepackage{paralist}
\usepackage{etoolbox}
\usepackage{stmaryrd}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{catchfilebetweentags}

\newcounter{mythmcounter}
\newcounter{mydefcounter}
\newcounter{myexpcounter}
\newtheorem{example}[myexpcounter]{Example}
\newtheorem{remark}[mythmcounter]{Remark}
\newtheorem{definition}[mydefcounter]{Definition}
\newtheorem{theorem}[mythmcounter]{Theorem}
\newtheorem{lemma}[mythmcounter]{Lemma}
\newtheorem{proposition}[mythmcounter]{Proposition}
\newtheorem*{lemma*}{Lemma}

% Formatting for source code & types
\definecolor{cmtclr}{rgb}{0.0,0.6,0.0}
\definecolor{kvdclr}{rgb}{0.0,0.0,0.6}
\definecolor{strclr}{rgb}{0.5,0.1,0.0}
\definecolor{prepclr}{rgb}{0.0,0.0,0.0}

\newcommand{\sep}[0]{\; | \;}
\newcommand{\kvd}[1]{\textnormal{\textcolor{kvdclr}{\ttfamily #1}}}
\newcommand{\str}[1]{\textnormal{\textcolor{strclr}{\ttfamily "#1"}}}
\newcommand{\prepk}[1]{\textnormal{\textcolor{prepclr}{\bfseries\sffamily #1}}}
\newcommand{\prepi}[1]{\textnormal{\textcolor{prepclr}{\ttfamily #1}}}
\newcommand{\ident}[1]{\textnormal{\sffamily #1}}
\newcommand{\cmt}[1]{\textit{\sffamily\textcolor{cmtclr}{#1}}}

\newcommand{\ctyp}[2]{C^{#1}#2}
\newcommand{\mtyp}[2]{M^{#1}#2}
\newcommand{\subst}[3]{#1[#2 \leftarrow #3]}

% Typing rule and typing statement (single line)
\newcommand{\tyrule}[3]{ \inference[\footnotesize{(\emph{#1})}~~]{#2}{#3} }
\newcommand{\tyruler}[3]{ \inference{#2}{#3}~~\footnotesize{(\emph{#1})} }

% Coeffect algebra
\definecolor{aclr}{rgb}{0.6,0.3,0.0}
\newcommand{\aclrd}[1]{\textcolor{aclr}{#1}}

% Coeffect algebra
\definecolor{cclr}{rgb}{0.0,0.5,0.0}
\newcommand{\cclrd}[1]{\textcolor{cclr}{#1}}

\newcommand{\czero}{ \textcolor{cclr}{ \mathsf{ign} } }
\newcommand{\cunit}{ \textcolor{cclr}{ \mathsf{use} } }
\newcommand{\cseq}{ \textcolor{cclr}{ \circledast }} 
\newcommand{\cpar}{ \textcolor{cclr}{\oplus} }
\newcommand{\czip}{ \textcolor{cclr}{\wedge} } % only used by flat coeffects
\newcommand{\cleq}{ \textcolor{cclr}{\leq} }
\newcommand{\cgeq}{ \textcolor{cclr}{\geq} }

\newcommand{\atimes}{ \textcolor{aclr}{\times} }
\newcommand{\aseq}{ \textcolor{aclr}{\circledast}} % Should be the same as \cseq 
\newcommand{\aparstr}{ \textcolor{aclr}{\oplus}} % Should be the same as \cseq

% Unified

\newcommand{\SH}{ {\textcolor{sclr}{S}} }
\newcommand{\SP}{ {\textcolor{sclr}{P}} }
\newcommand{\SHP}{ {\textcolor{sclr}{S\triangleleft P}} }
\newcommand{\sempty}{ {\textcolor{sclr}{ \hat{0}}} }
\newcommand{\sunit}{ {\textcolor{sclr}{\hat{1}}} }
\newcommand{\stimes}{ {\textcolor{sclr}{\diamond}} }
\newcommand{\sflat}{\star}

\newcommand{\azero}{ \textcolor{aclr}{\bot} }
\newcommand{\aunit}{ \alift{\cunit} }
\newcommand{\aweak}{ \alift{\czero} }

\newcommand{\azip}{ \textcolor{aclr}{ \mathbin{\rotatebox[origin=c]{-90}{$\ltimes$}} } }
\newcommand{\apar}{ \textcolor{aclr}{ \mathbin{\rotatebox[origin=c]{90}{$\ltimes$}} } }

\newcommand{\xtimes}{\hat{\times}}

\newcommand{\ctx}{\textit{ctx}}

% Ordinary context where colouring is done by hand 
\newcommand{\coctx}[2]{ #1 \,\text{\scriptsize @}\, {{\text{$#2$}}}  }

% Simple coeffect systems in the introduction
\newcommand{\cons}{\hspace{-0.15em}\times\hspace{-0.25em}} %\sctxclrd{+\hspace{-0.55em}+}}

\newcommand{\alift}[1]{ \textcolor{aclr}{\langle} #1 \textcolor{aclr}{\rangle}}

\definecolor{sclr}{rgb}{0.2,0,0.8}
\newcommand{\sclrd}[1]{ \textcolor{sclr}{#1} }

\newcommand{\C}{ {\textcolor{cclr}{\mathcal{C}}} }
\newcommand{\M}{ {\textcolor{cclr}{\mathcal{M}}} }

\newcommand{\alen}[1]{{\aclrd{\textit{len}(}#1\aclrd{)}}}
\newcommand{\slen}[1]{{\sclrd{\textit{len}(}#1\sclrd{)}}}
\newcommand{\xlen}[1]{{\textit{len}(#1)}}

\newcommand{\reduce}{\longrightarrow}

\newcommand{\restr}[2]{#1|_{#2}}
\newcommand{\narrow}[1]{\hspace{-0.5em} #1 \hspace{-0.65em}~}

\definecolor{todoclr}{rgb}{0.8,0,0.5}
\newcommand{\todo}[1]{\textcolor{todoclr}{ \begin{quotation} \noindent\textbf{TODO:} #1 \end{quotation} }}

@@

\newcommand{\figcaption}[1]{
  \vspace{0.5em}
  \noindent\makebox[\linewidth]{\rule{\textwidth}{0.5pt}} 
  \vspace{-2em}
  \caption{#1}
}
% Half line spacing around align
\newcommand{\zerodisplayskips}{%
  \setlength{\abovedisplayskip}{0.5em}
  \setlength{\belowdisplayskip}{0.5em}
  \setlength{\abovedisplayshortskip}{0.5em}
  \setlength{\belowdisplayshortskip}{0.5em}}
\appto{\normalsize}{\zerodisplayskips}
\appto{\small}{\zerodisplayskips}
\appto{\footnotesize}{\zerodisplayskips}

@@

\include{text/Titlepage} % Main title page

@@

\cleardoublepage\include{text/Declaration} % Publications from the thesis page

\cleardoublepage\include{text/Abstract} % Abstract page

@@

\include{text/Chapter01}
\include{text/Chapter02}
\include{text/Chapter03}
\include{text/Chapter04}
\include{text/Chapter05}
\include{text/Chapter06}
\include{text/Chapter07}

@@

@@

% \include{Chapters/Chapter0B} % Appendix B - empty template

@@

\appendix
\include{text/AppendixA}
\include{text/AppendixB}
